The Strong Gravitational Lens Finding Challenge

### 2018-02-12 paper.tex
Update on Overleaf.
edit

%\documentclass[useAMS,usenatbib]{mnras}
%\documentclass[useAMS,usenatbib]{aa}
\documentclass{aa}

@@

\keywords{gravitational lensing -- cosmology }

@@

Some automated algorithms have been developed in the past to detect lenses in images.  These have been designed to detect arc-like features \citep{2006astro.ph..6757A,2007AandA...472..341S, 2017AandA...597A.135B} and rings \citep{2014ApJ...785..144G,2014AandA...566A..63J}.  They have been applied to survey data and found of order 200 lenses \citep{2007AandA...461..813C,2012ApJ...749...38M,2016AandA...592A..75P}.  Another approach has been to use a lens modeling code to fit a model to all the candidates and pick out the ones that fit the model well \citep{2009ApJ...694..924M,2017arXiv170401585S}.

@@

For the ground based cases three configurations with highest area under ROC were III,IV and VI. Although the areas are very similar between IV and VI the last one is superior in the low fake positives end. Thus, for the Strong Lensing Challenge in the ground base sample, we used configuration VI. This final scheme is ilustraded in figure \ref{colorCASTCNN}.

>>>>

%\documentclass[onecolumn]{aa}
\documentclass{aa}

@@

@@

Some automated algorithms have been developed in the past to detect lenses in images.  These have been designed to detect arc-like 
features \citep{2006astro.ph..6757A,2007AnadA...472..341S, 2017AnadA...597A.135B} and rings 
\citep{2014ApJ...785..144G,2014AandA...566A..63J}.  They have been applied to survey data and found of order 200 lenses \citep{2007AandA...461..813C,2012ApJ...749...38M,2016AandA...592A..75P}.  Another approach has been to use a lens modeling code to fit a model to all the candidates and pick out the ones that fit the model well \citep{2009ApJ...694..924M,2017arXiv170401585S}.

@@

For the ground based cases three configurations with highest area under ROC were III,IV and VI. Although the areas are very similar between IV and VI the last one is superior in the low fake positives end. Thus, for the Strong Lensing Challenge in the ground base sample, we used configuration VI. This final scheme is illustrated in figure \ref{colorCASTCNN}.
